rotation_runs2019

### 2020-01-06 inst/documents/rotation_runs2019.Rmd
sorted 3 outputs : gens_rot_minus_seq    #total generations gens_u_rot_minus_seq  #gens under threshold mort_rot_minus_seq    #average mortality

nscenarios <- 100
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

@@

    #gens <- gens_under_thresh(dfres=dfres, threshold=threshold, mort_or_freq=linputs$mort_or_freq)

@@

    # to be able to save as for rot or seq
    if ( linputs$rot_interval == 0 ) {gens_seq <- as.numeric(gens)
                                      mort_seq <- cum_mort/gens_seq}
    else                             {gens_rot <- as.numeric(gens)
                                      mort_rot <- cum_mort/gens_rot}

@@

  # add scenario id column and difference onto results
  # df_in_out is one row
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, mort_rot=mort_rot, mort_seq=mort_seq, id=i))

  df_in_out$gens_rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

  df_in_out$mort_rot_minus_seq <- df_in_out$mort_rot - df_in_out$mort_seq

>>>>

nscenarios <- 20
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
id_expt <- 'D4'

@@

    gens_u <- gens_under_thresh(dfres=dfres, threshold=threshold, mort_or_freq=linputs$mort_or_freq)

@@

    # to be able to save as for rot or seq
    if ( linputs$rot_interval == 0 ) {gens_seq <- as.numeric(gens)
                                      gens_u_seq <- as.numeric(gens_u)
                                      mort_seq <- cum_mort/gens_seq}
    else                             {gens_rot <- as.numeric(gens)
                                      gens_u_rot <- as.numeric(gens_u)
                                      mort_rot <- cum_mort/gens_rot}

@@

  # add scenario id column and difference onto results
  # df_in_out is one row
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, 
                                        gens_u_rot=gens_u_rot, gens_u_seq=gens_u_seq,
                                        mort_rot=mort_rot, mort_seq=mort_seq, id=i))

  df_in_out$gens_rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq
  df_in_out$gens_u_rot_minus_seq <- df_in_out$gens_u_rot - df_in_out$gens_u_seq  
  df_in_out$mort_rot_minus_seq <- df_in_out$mort_rot - df_in_out$mort_seq

### 2020-01-06 inst/documents/rotations_notes.Rmd
sorted 3 outputs : gens_rot_minus_seq    #total generations gens_u_rot_minus_seq  #gens under threshold mort_rot_minus_seq    #average mortality

I think better to use mean mortality because it is more obviously meaningfull, and a potential way of comaparing runs even id they have different lengths or number of insecticides.

@@

>>>>

I think better to use mean mortality because it is more obviously meaningfull, and a potential way of comparing runs even if they have different lengths or number of insecticides.

# 2020-01-06 NEW YEAR

sorted 3 outputs :
gens_rot_minus_seq    #total generations
gens_u_rot_minus_seq  #gens under threshold
mort_rot_minus_seq    #average mortality

@@

# in rotation_runs2019.Rmd uncomment the line below and re-add calc gens-under-thresh
# gens <- gens_under_thresh(dfres=dfres, threshold=threshold, mort_or_freq=linputs$mort_or_freq)

*check on new outputs : tot-gens, mean-mort

Try some rotation_runs2019.Rmd with new outputs.
Get Sam to run new ones.
